Structural Divergence Analysis

### 2017-05-01 comparison_R0.Rmd
CA vs CM y comparaciones R0s

```{r prepare-data-CA}
data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
R0 = R0.CA

@@

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
CA.sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
CA.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))

@@

## dat with means and standard errors
d.CA = ddply(dat,c("dataset", "site.info"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})
```

```{r prepare-data-CM}
data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
R0 = R0.CM

@@

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
CM.sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
CM.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))

@@

## dat with means and standard errors
d.CM = ddply(dat,c("dataset", "site.info"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})
```

```{r comparison-mean-z.RSD-vs-site}
# CA
d = d.CA

@@

# save data
CA.mean.exp = d.exp$mean.z.RSD
CA.mean.mut = d.mut$mean.z.RSD
CA.mean.medium = d.medium$mean.z.RSD

CA.se.exp = d.exp$se.z.RSD
CA.se.mut = d.mut$se.z.RSD
CA.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

# CM
d = d.CM

@@

# save data
CM.mean.exp = d.exp$mean.z.RSD
CM.mean.mut = d.mut$mean.z.RSD
CM.mean.medium = d.medium$mean.z.RSD

CM.se.exp = d.exp$se.z.RSD
CM.se.mut = d.mut$se.z.RSD
CM.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

```{r plots, fig.cap = "yellow = active sites"}

# plot comparative profiles
par(pty = "s")

# exp
plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA <z.RSD> experimental", ylab = "CM <z.RSD> experimental")
abline(0, 1)
points(x = CA.mean.exp[active.site.index], y = CM.mean.exp[active.site.index], col = "yellow")

# mut
plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA <z.RSD> no-selection", ylab = "CM <z.RSD> no-selection")
abline(0, 1)
points(x = CA.mean.mut[active.site.index], y = CM.mean.mut[active.site.index], col = "yellow")

# medium
plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA <z.RSD> selection", ylab = "CM <z.RSD> selection")
abline(0, 1)
points(x = CA.mean.medium[active.site.index], y = CM.mean.medium[active.site.index], col = "yellow")
```

```{r correlations-CA-CM}

# calculate cors
r.exp = cor(CA.mean.exp, CM.mean.exp)
r.mut = cor(CA.mean.mut, CM.mean.mut)
r.medium = cor(CA.mean.medium, CM.mean.medium)

cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
                    "R" = c(r.exp, r.mut, r.medium))

knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM <Z-scores> profiles")
```

```{r sequence-profiles-comparison-CA}
# read experimental data obtained from ConsurfDB
consurf = read.csv(score.fname, sep = ";")
score = consurf$SCORE

# read simulated data
## no sel
CA.sim.data.mut = read.csv(CA.sim.data.mut.fname)
mut.site.mut = CA.sim.data.mut$site
accept.mut = CA.sim.data.mut$accept

## medium sel
CA.sim.data.medium.sel = read.csv(CA.sim.data.medium.sel.fname)
mut.site.medium.sel = CA.sim.data.medium.sel$site
accept.medium.sel = CA.sim.data.medium.sel$accept

@@

# calculate CN
CN.CA = CA.sim.data.mut$CN
CN = c()

for (i in (1:n.sites)) {
  CN[i] = CN.CA[which(mut.site.mut == i)][1]
}

@@

cor.df = data.frame("Comparison CA" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

cor.df = data.frame("Comparison CA" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

```{r sequence-profiles-comparison-CM}
# read experimental data obtained from ConsurfDB
consurf = read.csv(score.fname, sep = ";")
score = consurf$SCORE

# read simulated data
## no sel
CM.sim.data.mut = read.csv(CM.sim.data.mut.fname)
mut.site.mut = CM.sim.data.mut$site
accept.mut = CM.sim.data.mut$accept

## medium sel
CM.sim.data.medium.sel = read.csv(CM.sim.data.medium.sel.fname)
mut.site.medium.sel = CM.sim.data.medium.sel$site
accept.medium.sel = CM.sim.data.medium.sel$accept

@@

# correct indexes
mut.site.mut = mut.site.mut - n.sites
mut.site.medium.sel = mut.site.medium.sel - n.sites

# calculate CN
CN.CM = CM.sim.data.mut$CN
CN = c()

for (i in (1:n.sites)) {
  CN[i] = CN.CM[which(mut.site.mut == i)][1]
}

@@

cor.df = data.frame("Comparison CM" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

cor.df = data.frame("Comparison CM" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

```{r structure-profiles-CN-comparison}
# CA
d = d.CA

## calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")

@@

cor.df = data.frame("Comparison CA" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

@@

# CM
d = d.CM

## calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")

@@

cor.df = data.frame("Comparison CM" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

@@

### Structure - normal modes 
```{r prepare-data-Pn-CA}
data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
R0 = R0.CA

@@

CA.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                       data.frame("dataset" = "mut", modeComparison.mut),
                                       data.frame("dataset" = "medium", modeComparison.medium))

dat = CA.modeComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# calculate dataset of means

d.CA = ddply(dat,c("dataset", "mode"), function(x) {
       median.Pn = median(x$Pn)
       Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
       Pn.median.min = Pn.median.ci[1]
       Pn.median.max = Pn.median.ci[2]
       data.frame(Pn.median.min, Pn.median.max, median.Pn)
})
```

```{r prepare-data-Pn-CM}
data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
R0 = R0.CM

@@

CM.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                       data.frame("dataset" = "mut", modeComparison.mut),
                                       data.frame("dataset" = "medium", modeComparison.medium))

dat = CM.modeComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

@@

d.CM = ddply(dat,c("dataset", "mode"), function(x) {
       median.Pn = median(x$Pn)
       Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
       Pn.median.min = Pn.median.ci[1]
       Pn.median.max = Pn.median.ci[2]
       data.frame(Pn.median.min, Pn.median.max, median.Pn)
})
```

```{r comparison-median.Pn-vs-mode}
# CA
d = d.CA

@@

# save data
CA.mean.exp = d.exp$median.Pn
CA.mean.mut = d.mut$median.Pn
CA.mean.medium = d.medium$median.Pn

CA.se.exp = d.exp$se.z.RSD
CA.se.mut = d.mut$se.z.RSD
CA.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

# save data
CM.mean.exp = d.exp$median.Pn
CM.mean.mut = d.mut$median.Pn
CM.mean.medium = d.medium$median.Pn

CM.se.exp = d.exp$se.z.RSD
CM.se.mut = d.mut$se.z.RSD
CM.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

# exp
plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA median.Pn experimental", ylab = "CM median.Pn experimental")
abline(0, 1)

# mut
plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA median.Pn no-selection", ylab = "CM median.Pn no-selection")
abline(0, 1)

# medium
plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA median.Pn selection", ylab = "CM median.Pn selection")
abline(0, 1)
```

```{r correlations-CA-CM-Pn}

# calculate cors
r.exp = cor(CA.mean.exp, CM.mean.exp)
r.mut = cor(CA.mean.mut, CM.mean.mut)
r.medium = cor(CA.mean.medium, CM.mean.medium)

cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
                    "R" = c(r.exp, r.mut, r.medium))

knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM median.Pn profiles")
```

### Dynamics - MSF

```{r prepare-data-square.dif.MSF-CA}
data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
R0 = R0.CA

@@

CA.siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                       data.frame("dataset" = "mut", siteComparison.mut),
                                       data.frame("dataset" = "medium", siteComparison.medium))

CA.siteComparison.all.datasets = ddply(CA.siteComparison.all.datasets, c("dataset", "protein"), mutate,
          "r.SDF" = rank(square.dif.MSF, na.last = "keep"))

dat = CA.siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# calculate dataset of means
d.CA = ddply(dat, c("dataset", "site"), function(x) {
       mean.r.SDF = mean(x$r.SDF, na.rm = T)
       data.frame(mean.r.SDF)
})
```

```{r prepare-data-square.dif.MSF-CM}
data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
R0 = R0.CM

@@

CM.siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                       data.frame("dataset" = "mut", siteComparison.mut),
                                       data.frame("dataset" = "medium", siteComparison.medium))

CM.siteComparison.all.datasets = ddply(CM.siteComparison.all.datasets, c("dataset", "protein"), mutate,
          "r.SDF" = rank(square.dif.MSF, na.last = "keep"))

dat = CM.siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# calculate dataset of means
d.CM = ddply(dat, c("dataset", "site"), function(x) {
       mean.r.SDF = mean(x$r.SDF, na.rm = T)
       data.frame(mean.r.SDF)
})
```

```{r comparison-mean.r.SDF-site}
# CA
d = d.CA

@@

# save data
CA.mean.exp = d.exp$mean.r.SDF
CA.mean.mut = d.mut$mean.r.SDF
CA.mean.medium = d.medium$mean.r.SDF

CA.se.exp = d.exp$se.z.RSD
CA.se.mut = d.mut$se.z.RSD
CA.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

# save data
CM.mean.exp = d.exp$mean.r.SDF
CM.mean.mut = d.mut$mean.r.SDF
CM.mean.medium = d.medium$mean.r.SDF

CM.se.exp = d.exp$se.z.RSD
CM.se.mut = d.mut$se.z.RSD
CM.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

# exp
plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA mean.r.SDF experimental", ylab = "CM mean.r.SDF experimental")
abline(0, 1)

# mut
plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA mean.r.SDF no-selection", ylab = "CM mean.r.SDF no-selection")
abline(0, 1)

# medium
plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA mean.r.SDF selection", ylab = "CM mean.r.SDF selection")
abline(0, 1)
```

```{r correlations-CA-CM-MSF}
# calculate cors
r.exp = cor(CA.mean.exp, CM.mean.exp)
r.mut = cor(CA.mean.mut, CM.mean.mut)
r.medium = cor(CA.mean.medium, CM.mean.medium)

cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
                    "R" = c(r.exp, r.mut, r.medium))

knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM mean.r.SDF profiles")
```

### Dynamics - normal modes (nH)
```{r prepare-data-nH-CA}
data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
R0 = R0.CA

@@

CA.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                       data.frame("dataset" = "mut", modeComparison.mut),
                                       data.frame("dataset" = "medium", modeComparison.medium))

dat = CA.modeComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# calculate dataset of means

d.CA = ddply(dat,c("dataset", "mode"), function(x) {
       mean.nH = mean(x$nH)
       data.frame(mean.nH)
})
```

```{r compare-data-nH-CM}
data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
R0 = R0.CM

@@

# save data
CA.mean.exp = d.exp$mean.nH
CA.mean.mut = d.mut$mean.nH
CA.mean.medium = d.medium$mean.nH

>>>>

```{r prepare-data-R0.1}
R0 = R0.1

@@

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
R0.1.sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
R0.1.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))

@@

## dat with means and standard errors
d.R0.1 = ddply(dat,c("dataset", "site.info"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})
```

```{r prepare-data-R0.2}
R0 = R0.2

@@

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
R0.2.sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
R0.2.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))

@@

## dat with means and standard errors
d.R0.2 = ddply(dat,c("dataset", "site.info"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})
```

```{r comparison-mean-z.RSD-vs-site}
# R0.1
d = d.R0.1

@@

# save data
R0.1.mean.exp = d.exp$mean.z.RSD
R0.1.mean.mut = d.mut$mean.z.RSD
R0.1.mean.medium = d.medium$mean.z.RSD

R0.1.se.exp = d.exp$se.z.RSD
R0.1.se.mut = d.mut$se.z.RSD
R0.1.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison R0.1" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

# R0.2
d = d.R0.2

@@

# save data
R0.2.mean.exp = d.exp$mean.z.RSD
R0.2.mean.mut = d.mut$mean.z.RSD
R0.2.mean.medium = d.medium$mean.z.RSD

R0.2.se.exp = d.exp$se.z.RSD
R0.2.se.mut = d.mut$se.z.RSD
R0.2.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison R0.2" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

```{r plots, fig.cap= "yellow = active sites"}
# plot comparative profiles
par(pty = "s")

# exp
plot(x = R0.1.mean.exp, y = R0.2.mean.exp, xlab = "R0.1 <z.RSD> experimental", ylab = "R0.2 <z.RSD> experimental")
abline(0, 1)
points(x = R0.1.mean.exp[active.site.index], y = R0.2.mean.exp[active.site.index], col = "yellow")

# mut
plot(x = R0.1.mean.mut, y = R0.2.mean.mut, xlab = "R0.1 <z.RSD> no-selection", ylab = "R0.2 <z.RSD> no-selection")
abline(0, 1)
points(x = R0.1.mean.mut[active.site.index], y = R0.2.mean.mut[active.site.index], col = "yellow")

# medium
plot(x = R0.1.mean.medium, y = R0.2.mean.medium, xlab = "R0.1 <z.RSD> selection", ylab = "R0.2 <z.RSD> selection")
abline(0, 1)
points(x = R0.1.mean.medium[active.site.index], y = R0.2.mean.medium[active.site.index], col = "yellow")
```

```{r correlations-R0.1-R0.2}
# calculate cors
r.exp = cor(R0.1.mean.exp, R0.2.mean.exp)
r.mut = cor(R0.1.mean.mut, R0.2.mean.mut)
r.medium = cor(R0.1.mean.medium, R0.2.mean.medium)

cor.df = data.frame("Comparison" = c("exp R0.1 vs R0.2", "no-selection R0.1 vs R0.2", "selection R0.1 vs R0.2"),
                    "R" = c(r.exp, r.mut, r.medium))

knitr::kable(cor.df, digits = 2, caption = "Correlation between R0.1 and R0.2 <Z-scores> profiles")
```

```{r sequence-profiles-comparison}
# read experimental data obtained from ConsurfDB
consurf = read.csv(score.fname, sep = ";")
score = consurf$SCORE

# read simulated data
## no sel
R0.1.sim.data.mut = read.csv(R0.1.sim.data.mut.fname)
mut.site.mut = R0.1.sim.data.mut$site
accept.mut = R0.1.sim.data.mut$accept

## medium sel
R0.1.sim.data.medium.sel = read.csv(R0.1.sim.data.medium.sel.fname)
mut.site.medium.sel = R0.1.sim.data.medium.sel$site
accept.medium.sel = R0.1.sim.data.medium.sel$accept

@@

# correct indexes
if (data.dir == "OUT/out_subset_CM_ANM") {
  mut.site.mut = mut.site.mut - n.sites
  mut.site.medium.sel = mut.site.medium.sel - n.sites
}

# calculate CN
CN.R0.1 = R0.1.sim.data.mut$CN
CN = c()

for (i in (1:n.sites)) {
  CN[i] = CN.R0.1[which(mut.site.mut == i)][1]
}

@@

cor.df = data.frame("Comparison R0.1" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

cor.df = data.frame("Comparison R0.1" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

print("<paccept selection>")
print(mean(p.accept.medium.sel))

# read experimental data obtained from ConsurfDB
consurf = read.csv(score.fname, sep = ";")
score = consurf$SCORE

# read simulated data
## no sel
R0.2.sim.data.mut = read.csv(R0.2.sim.data.mut.fname)
mut.site.mut = R0.2.sim.data.mut$site
accept.mut = R0.2.sim.data.mut$accept

## medium sel
R0.2.sim.data.medium.sel = read.csv(R0.2.sim.data.medium.sel.fname)
mut.site.medium.sel = R0.2.sim.data.medium.sel$site
accept.medium.sel = R0.2.sim.data.medium.sel$accept

@@

# correct indexes
if (data.dir == "OUT/out_subset_CM_ANM") {
  mut.site.mut = mut.site.mut - n.sites
  mut.site.medium.sel = mut.site.medium.sel - n.sites
}

# calculate CN
CN.R0.2 = R0.2.sim.data.mut$CN
CN = c()

for (i in (1:n.sites)) {
  CN[i] = CN.R0.2[which(mut.site.mut == i)][1]
}

@@

cor.df = data.frame("Comparison R0.2" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

cor.df = data.frame("Comparison R0.2" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

```{r structure-profiles-CN-comparison}

# R0.1
d = d.R0.1

@@

cor.df = data.frame("Comparison R0.1" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

@@

# R0.2
d = d.R0.2

@@

cor.df = data.frame("Comparison R0.2" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

@@

### Structure - normal modes 
```{r prepare-data-Pn-R0.1}
R0 = R0.1

@@

R0.1.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                       data.frame("dataset" = "mut", modeComparison.mut),
                                       data.frame("dataset" = "medium", modeComparison.medium))

dat = R0.1.modeComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

d.R0.1 = ddply(dat,c("dataset", "mode"), function(x) {
       median.Pn = median(x$Pn)
       Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
       Pn.median.min = Pn.median.ci[1]
       Pn.median.max = Pn.median.ci[2]
       data.frame(Pn.median.min, Pn.median.max, median.Pn)
})
```

```{r prepare-data-Pn-R0.2}
R0 = R0.2

@@

R0.2.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                       data.frame("dataset" = "mut", modeComparison.mut),
                                       data.frame("dataset" = "medium", modeComparison.medium))

dat = R0.2.modeComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

@@

d.R0.2 = ddply(dat,c("dataset", "mode"), function(x) {
       median.Pn = median(x$Pn)
       Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
       Pn.median.min = Pn.median.ci[1]
       Pn.median.max = Pn.median.ci[2]
       data.frame(Pn.median.min, Pn.median.max, median.Pn)
})
```

```{r comparison-median.Pn-vs-mode}
# R0.1
d = d.R0.1

@@

# save data
R0.1.mean.exp = d.exp$median.Pn
R0.1.mean.mut = d.mut$median.Pn
R0.1.mean.medium = d.medium$median.Pn

R0.1.se.exp = d.exp$se.z.RSD
R0.1.se.mut = d.mut$se.z.RSD
R0.1.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison R0.1" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

# save data
R0.2.mean.exp = d.exp$median.Pn
R0.2.mean.mut = d.mut$median.Pn
R0.2.mean.medium = d.medium$median.Pn

R0.2.se.exp = d.exp$se.z.RSD
R0.2.se.mut = d.mut$se.z.RSD
R0.2.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison R0.2" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

# exp
plot(x = R0.1.mean.exp, y = R0.2.mean.exp, xlab = "R0.1 median.Pn experimental", ylab = "R0.2 median.Pn experimental")
abline(0, 1)

# mut
plot(x = R0.1.mean.mut, y = R0.2.mean.mut, xlab = "R0.1 median.Pn no-selection", ylab = "R0.2 median.Pn no-selection")
abline(0, 1)

# medium
plot(x = R0.1.mean.medium, y = R0.2.mean.medium, xlab = "R0.1 median.Pn selection", ylab = "R0.2 median.Pn selection")
abline(0, 1)
```

```{r correlations-R0.1-R0.2-Pn}
# calculate cors
r.exp = cor(R0.1.mean.exp, R0.2.mean.exp)
r.mut = cor(R0.1.mean.mut, R0.2.mean.mut)
r.medium = cor(R0.1.mean.medium, R0.2.mean.medium)

cor.df = data.frame("Comparison" = c("exp R0.1 vs R0.2", "no-selection R0.1 vs R0.2", "selection R0.1 vs R0.2"),
                    "R" = c(r.exp, r.mut, r.medium))

knitr::kable(cor.df, digits = 2, caption = "Correlation between R0.1 and R0.2 median.Pn profiles")
```

### Dynamics - MSF 
```{r prepare-data-square.dif.MSF-R0.1}
R0 = R0.1

@@

R0.1.siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                       data.frame("dataset" = "mut", siteComparison.mut),
                                       data.frame("dataset" = "medium", siteComparison.medium))

R0.1.siteComparison.all.datasets = ddply(R0.1.siteComparison.all.datasets, c("dataset", "protein"), mutate,
          "r.SDF" = rank(square.dif.MSF, na.last = "keep"))

dat = R0.1.siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# calculate dataset of means
d.R0.1 = ddply(dat, c("dataset", "site"), function(x) {
       mean.r.SDF = mean(x$r.SDF, na.rm = T)
       data.frame(mean.r.SDF)
})
```

```{r prepare-data-square.dif.MSF-R0.2}
R0 = R0.2

@@

R0.2.siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                       data.frame("dataset" = "mut", siteComparison.mut),
                                       data.frame("dataset" = "medium", siteComparison.medium))

R0.2.siteComparison.all.datasets = ddply(R0.2.siteComparison.all.datasets, c("dataset", "protein"), mutate,
          "r.SDF" = rank(square.dif.MSF, na.last = "keep"))

dat = R0.2.siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# calculate dataset of means
d.R0.2 = ddply(dat, c("dataset", "site"), function(x) {
       mean.r.SDF = mean(x$r.SDF, na.rm = T)
       data.frame(mean.r.SDF)
})
```

```{r comparison-mean.r.SDF-site}
# R0.1
d = d.R0.1

@@

# save data
R0.1.mean.exp = d.exp$mean.r.SDF
R0.1.mean.mut = d.mut$mean.r.SDF
R0.1.mean.medium = d.medium$mean.r.SDF

R0.1.se.exp = d.exp$se.z.RSD
R0.1.se.mut = d.mut$se.z.RSD
R0.1.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison R0.1" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

# save data
R0.2.mean.exp = d.exp$mean.r.SDF
R0.2.mean.mut = d.mut$mean.r.SDF
R0.2.mean.medium = d.medium$mean.r.SDF

R0.2.se.exp = d.exp$se.z.RSD
R0.2.se.mut = d.mut$se.z.RSD
R0.2.se.medium = d.medium$se.z.RSD

cor.df = data.frame("Comparison R0.2" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

@@

# exp
plot(x = R0.1.mean.exp, y = R0.2.mean.exp, xlab = "R0.1 mean.r.SDF experimental", ylab = "R0.2 mean.r.SDF experimental")
abline(0, 1)

# mut
plot(x = R0.1.mean.mut, y = R0.2.mean.mut, xlab = "R0.1 mean.r.SDF no-selection", ylab = "R0.2 mean.r.SDF no-selection")
abline(0, 1)

# medium
plot(x = R0.1.mean.medium, y = R0.2.mean.medium, xlab = "R0.1 mean.r.SDF selection", ylab = "R0.2 mean.r.SDF selection")
abline(0, 1)
```

```{r correlations-R0.1-R0.2-MSF}
# calculate cors
r.exp = cor(R0.1.mean.exp, R0.2.mean.exp)
r.mut = cor(R0.1.mean.mut, R0.2.mean.mut)
r.medium = cor(R0.1.mean.medium, R0.2.mean.medium)

cor.df = data.frame("Comparison" = c("exp R0.1 vs R0.2", "no-selection R0.1 vs R0.2", "selection R0.1 vs R0.2"),
                    "R" = c(r.exp, r.mut, r.medium))

knitr::kable(cor.df, digits = 2, caption = "Correlation between R0.1 and R0.2 mean.r.SDF profiles")
```

### Dynamics - normal modes (nH)

```{r prepare-data-nH-R0.1}
R0 = R0.1

@@

R0.1.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                       data.frame("dataset" = "mut", modeComparison.mut),
                                       data.frame("dataset" = "medium", modeComparison.medium))

dat = R0.1.modeComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# calculate dataset of means
d.R0.1 = ddply(dat,c("dataset", "mode"), function(x) {
       mean.nH = mean(x$nH)
       data.frame(mean.nH)
})
```

```{r prepare-data-nH-R0.2}
R0 = R0.2

@@

# save data
R0.1.mean.exp = d.exp$mean.nH
R0.1.mean.mut = d.mut$mean.nH
R0.1.mean.medium = d.medium$mean.nH
